Data Management for LSST Special Programs

### 2024-03-26 sec_sci.tex
update obs mode text

\textbf{Observing Mode Labels -- } 
Based on the scheduler mode at the time of the observation
(i.e., survey cadence or strategy).
To be applied by the Survey Scheduler team via the observations scheduler.
Observing mode labels might include, e.g., WFD, DDF, TOO, mini-survey name, or other 
options like engineering, commissioning, and director's discretionary.
Observing mode labels should be propagated to single-visit processed and 
difference images and catalog sources.
It would not make sense to propagate observing mode labels to deep coadds or 
object tables, as these data products could be a mix of modes.
It is left to the discretion of the Survey Scheduler team whether more than one
observing mode labels might be applied at a time and, e.g., held in a single string as a CSV.

A given image would probably only have one observing mode label

>>>>

\textbf{Observing Mode Labels -- } 
Applied to a visit based on the scheduler mode at the time of the observation
(i.e., survey cadence or strategy).

To be applied by the Survey Scheduler team via the observations scheduler.
Observing mode labels might include, e.g., WFD, DDF, TOO, mini-survey name, or other 
options like engineering, commissioning, and director's discretionary.
A given image would probably only have one observing mode label, but
it is left to the discretion of the Survey Scheduler team whether more than one
observing mode labels might be applied at a time and, e.g., held in a single string as a CSV.

The observing mode labels should be available to users as query constraints for
all single-visit processed and difference images and catalog sources,
via both the butler and the TAP service.
It would not make sense to apply observing mode labels to deep coadds or 
object tables, as these data products could be a mix of modes.
